<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@

@@

@@

![](templates/figures/templates_ants_colleagues.png)
## longitudinal

>>>>

a pride: common way of doing things

@@

... developers can be blind to doc deficiencies

while users are blind to what we provide!

@@

see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)

@@

![](templates/figures/templates_ants_colleagues.png)

## longitudinal
